\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}
\section{Crooke's Tube & Electrons}
\href{https://www.youtube.com/watch?v=Ka3v5dIQGOI}{LHSAtkins, \textit{Crooke's Tube & Electrons}, USA, 13.09.2013}\\
\subsection{Retranscription}
\begin{enumerate}
    \item So what I'm gonna show you today is how they figures out that Dalton's model isn't complete.
    \item \hspace*{1cm} \emph{ français :} Donc ce que je vais vous montrer aujourd'hui est comment on a démontré que le modèle de Dalton n'est pas complet.
    \item It begans with this thing called a Crooke's tube.
     \item \hspace*{1cm} \emph{ français :} Cela commence avec une chose appelé le tube de Crookes.
    \item Anyone have seen a Crooke's tube before.
      \item \hspace*{1cm} \emph{ français :} Tout le monde a déjà vu le tube de  Crookes avant.
    \item This is the first tube what it is ?
     \item \hspace*{1cm} \emph{ français  :} C'est le premier tube.
    \item It's a tube of glass that's mostly evacuated, meaning that most of the air is taken out of it.
     \item \hspace*{1cm} \emph{ français :} C'est un tube en verre qui est principalement évacué, c'est-à-dire que la plupart de son air en a été sorti.
    \item It's got an electrode on this side and an electrode on that side.
     \item \hspace*{1cm} \emph{ français :} Il y a une électrode sur ce côté et une électrode sur ce côté.
    \item If you look on the inside of it there's a white screen.
     \item \hspace*{1cm} \emph{ français :} Si vous regardez à l'intérieur, il y a un écran blanc.
    \item The white screen is there for reasons
    I'll show you in a moment.
     \item \hspace*{1cm} \emph{ français :} L'écran blanc est là pour des raisons que je vous montrerais dans un moment.
    \item This is a Tesla coil.
     \item \hspace*{1cm} \emph{ français :} Ceci est une bobine de Tesla.
    \item Tesla coils generate lots of voltage.
     \item \hspace*{1cm} \emph{ français :} Les bobines de Tesla génèrent beaucoup de voltages.
    \item Right now there is a magnet inside of here the spinning.
     \item \hspace*{1cm} \emph{ français :} À partir de maintenant, il y a un aimant à l'intérieur qui tourne.
    \item It's got some wires around that magnet to generating a lot of voltage (1:09) voltage has been a strong magnet in fact if I hold another magnet up here.
     \item \hspace*{1cm} \emph{ français :} Il y a quelques fils autour de l'aimant pour génèrer beaucoup de voltages qui ont en fait un aimant puissant, si je tiens un autre aimant ici.
    \item I can feel it vibrating from the spinning of the magnet.
     \item \hspace*{1cm} \emph{ français :} Je peux sentir l'aimant tourné par sa vibration.
    \item It's a kind of like, your Rumble is on your game controller.
     \item \hspace*{1cm} \emph{ français :} C'est une sorte de, vos Rumble sur vos manettes de jeu.
    \item But this is generating a lot of electricity.
     \item \hspace*{1cm} \emph{ français :} Mais cela génère beaucoup d'électricité.
    \item (1:30) Now you can see that if you hold...
     \item \hspace*{1cm} \emph{ français :} Maintenant vous pouvez voir, si vous tenez...
    \item *electrical decharges
     \item \hspace*{1cm} \emph{ français :} * décharges électriques
    \item People always ask what will happen if you touch.
     \item \hspace*{1cm} \emph{ français :} Les gens demandent toujours ce qu'ils se passent quand ça nous touche.
    \item It's the answer, I'm not dead.
     \item \hspace*{1cm} \emph{ français :} La réponse, je ne suis pas mort.
    \item Uncomfortable
     \item \hspace*{1cm} \emph{ français :} Incomfortable.
    \item But in any case, here's what happens when you fold it across approach to.
     \item \hspace*{1cm} \emph{ français :} Mais dans tout les cas, voilà ce qu'il se passe quand vous le pliez et vous l'approchez.
    \item If I see that you see it over there on that side.
     \item \hspace*{1cm} \emph{ français :}Si je vois que vous voyez de ce côté.
    \item (2:11) Pretty cool
    \item \hspace*{1cm} \emph{ français :} Bien
    \item I actually can't see it from my side but I assume you're saying a straight green line.
     \item \hspace*{1cm} \emph{ français :} Je ne peux pas voir de ce côté mais je conclue que vous dites qu'il y a une ligne droite verte.
    \item Mostly because I'm looking from behind.
     \item \hspace*{1cm} \emph{ français :} Surtout parce que je regarde de derrière.
    \item That white screen only on the front, it's set up to be viewed frome one side only.
     \item \hspace*{1cm} \emph{ français :} Cet écran blanc est seulement de ce côté, on ne peut que voir depuis celui-là.
    \item (2:32) Now, this is kind of interesting watch this.
     \item \hspace*{1cm} \emph{ français :} Maintenant, c'est un type d'expérience intéréssante.
    \item *deviation of the line
     \item \hspace*{1cm} \emph{ français :} *déviation de la ligne
    \item Is anything happening ?
     \item \hspace*{1cm} \emph{ français :}Il se passe quelque chose ?
    \item What's happening, it's following the magnet reacting to the magnet is deflecting the magnet.
     \item \hspace*{1cm} \emph{ français :}Qu'est-ce qu'il se passe, cela suit l'aimant qui réagit à l'aimant qui déviant l'aimant.
    \item So that's kind of interesting keep that going.
     \item \hspace*{1cm} \emph{ français :} C'est un type de chose intré
    \item I got a huge one other thing to compare that to I have a light here.
     \item \hspace*{1cm} \emph{ français }
    \item I'm gonna pass this light so it's a laser light.
     \item \hspace*{1cm} \emph{ français }
    \item (3:40) The green laser light up that.
     \item \hspace*{1cm} \emph{ français }
    \item (3:44) Don't film over there we go, so you see that laser lights is there.
     \item \hspace*{1cm} \emph{ français }
    \item (3:49) What will happen to it when I get it close to the magnet deflect away, he says.
     \item \hspace*{1cm} \emph{ français }
    \item (4:04)Is it deflecting away there's no effect on the mag a magnet has no effect on writing.
     \item \hspace*{1cm} \emph{ français }
    \item (4:10) So why does some white get deflected by a magnet and some other light doesn't why is that ?
     \item \hspace*{1cm} \emph{ français }
    \item (4:14) What's the primary difference ? 
     \item \hspace*{1cm} \emph{ français }
    \item (4:34) The answer is : they might know what is different about that light fro
     \item \hspace*{1cm} \emph{ français }
    \item (4:38) Why are they different ? What's one hand that the other doesn't.
     \item \hspace*{1cm} \emph{ français }
    \item (4:45) This specific word we're looking for here batteries.
     \item \hspace*{1cm} \emph{ français }
    \item (4:58) Batteries are electricity, but she kind of got the right word.
     \item \hspace*{1cm} \emph{ français }
    \item (5:01) Their charge is the key, it turns out that this light isn't charged at all, it's just light.
     \item \hspace*{1cm} \emph{ français }
    \item (5:05) This is obviously, it's charged because that's what magnets do is they deflect charges they'll either make things go toward them.
     \item \hspace*{1cm} \emph{ français }
    \item (5:16) Or away from them depending on which plus or minus or the North or South pole of the magnet.
     \item \hspace*{1cm} \emph{ français }
    \item (5:19) So what we have discovered, here is that there's something going through here that is charged somethings jumping out of this metal electrode into this metal electrode.
     \item \hspace*{1cm} \emph{ français }
    \item (5:31) That is charged in since these metal electrodes are made of atoms, then atoms must have something charged in them.
     \item \hspace*{1cm} \emph{ français }
    \item (5:45) And JJ. Thompson is a scientist on our paper that we researched, this is what he discovered.
     \item \hspace*{1cm} \emph{ français }
    \item (5:50) He discovered that these things, the atoms had these charges inside them called : electrons.
     \item \hspace*{1cm} \emph{ français }
    \item (5:58) Those are actually electrons going across there and JJ Thompson discovered them.
     \item \hspace*{1cm} \emph{ français }
     
\end{enumerate}

\end{document}